---
title: "Parler_Data_Processing"
author: "Dominik Bär"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE, message = FALSE, results = "hide")
```

# ##################################################################################################################
#    File to sample QAnon users from data_users and retrieve their posts/comments from parler_data
#        - Find unique users that posted
#        - Match users with metadata
#        - Identify QAnon users based on "biography"
#        - Sample appropriate number of QAnon and non-QAnon users and retrieve thir posts/comments from parler_data
# ##################################################################################################################

# Libraries

```{r library, include=FALSE}

library(tidyverse)
library(lubridate)
library(corpus)
library(tidytext)
library(textclean)
library(stopwords)
library(doParallel)
library(furrr)
library(udpipe)
library(cld2)
library(cld3)
library(sentimentr)
library(caret)
library(smotefamily)

#Python setup
library(reticulate)
imbllearn = reticulate::import("imblearn")

```

# Directories

```{r paths, include = FALSE}

# Set Seed
set.seed(1234)

# Input data
path_input <- "./../data/input/"
# Output data
path_output <- "./../data/output/"

# Data content
file_list_content <- list.files(path =  str_c(path_input, "parler_data/"), pattern = "*.Rdata")
# Data user 
file_list_user <- list.files(path =  str_c(path_input, "parler_users/"), pattern = "*.ndjson") 
# Content by user
file_list_content_by_user <- list.files(path = str_c(path_input, "parleys_user/"), pattern = "*.RDS")

```

# Important variables

```{r, include = FALSE}

# Important variables content
content_vars <- c("id", "comments", "body", "bodywithurls", "createdAtformatted", "creator", "datatype", "hashtags", "media", "upvotes", "impressions", "reposts", "downvotes", "score", "urls")

# Important variables user
user_vars <- c("id", "key", "bio", "comments", "datatype", "user_followers", "user_following", "joined", "likes", "posts")

# Define vector with QAnon indicators
qanon_indicator <- c("anons", "anon", "qanons", "qanon", " q ", "thegreatawakening", "greatawakening", "wwg1wga", "wgaworldwide", "qarmy", "obamagate", "pizzagate", "savethechildren", "saveourchildren", "taketheoath", "deep state", "deepstate", "deepstatecoup", "deepstatecabal", "deepstateexposed", "plandemic", "scamdemic", "sheepnomore", "adrenochrome", "thestorm", "followthewhiterabbit", "downtherabbithole", "thesepeoplearesick", "wearethenewsnow", "pizzagateisreal", "thestormisuponus", "newworldorder", "darktolight", "clintonbodycount")

# Import udpipe model for data annotation ("english")
udmodel <- udpipe_download_model(language = "english")
udmodel_en <- udpipe_load_model(file = udmodel$file_model)

# Remove "q" from stopwords
stop <- stop_words[stop_words$word != "q", ]

# Vector of important POS-tags
pos_tags <- c("NOUN", "PROPN", "PRON", "ADJ", "ADV", "VERB", "AUX", "ADP", "DET")

# Proportion of data in training sample
p_train <- 0.8

```

# Feature names

```{r}

# Vector with feature names
names_features_user <- c("account_age", "user_followers", "user_following" , "user_posts", "user_comments", "freq_upvotes_posts", "freq_impressions", "freq_upvotes_comments", "freq_downvotes_comments")
names_features_stylistic <- c("freq_handle_user", "freq_hash_user", "freq_pos_user", "freq_long_words_user", "freq_urls", "user_sentiment")
names_features_text <- str_c("text", c(0:383))
names_features_all <- c(names_features_user, names_features_stylistic, names_features_text)

```

# Dataset names

```{r}

# List of samples
data_names <- c("ADASYN", "SmoteTomek")

```

# Customized functions

```{r, include = False}

# Read specific columns of Rdata files
read_rdata_column <- function(filename, col_name){
  load(filename)
  out <- dta %>%
    select(all_of(col_name))
  return(out)
}

# Read specific columns of Rdata files and join with dataset
read_rdata_column_join <- function(filename, col_name, join_dta, key){
  load(filename) 
  out <- dta %>%
    select(all_of(col_name)) %>%
    inner_join(join_dta, by = key)
  return(out)
}

# Read specific columns of ndjson files
read_ndjson_column <- function(filename, col_name){
  data <- read_ndjson(filename, mmap = TRUE) %>%
    select(all_of(col_name))
}

# Annotate splitted text data
annotate_splits <- function(x, var) {
  x <- udpipe_annotate(udmodel_en, x[[var]])
  out <- as.data.frame(x) %>% select(doc_id, token, upos)
  return(out)
}

```

# Import content and identify unique users 

```{r, include = FALSE}

# Load content
content <- file_list_content %>%
  map(~ str_c(path_input, "parler_data/", .x)) %>%
  future_map(~ read_rdata_column(.x, c("creator", "body")), .progress = TRUE)

# Select unique users, i.e. users posted at least once & body != ""
unique_user_content <- content %>%
  bind_rows() %>%
  #select(creator, body) %>%
  distinct(creator)

save(unique_user_content, file = str_c(path_output, "unique_user_content.Rdata"))

```

# Load user metadata for unique users

```{r, include = FALSE}

user_data <- file_list_user %>%
  map(~ str_c(path_input, "parler_users/", .x)) %>%
  future_map(~ read_ndjson_column(.x, col_name = user_vars), .progress = TRUE) %>%
  bind_rows()

save(user_data, file = str_c(path_output, "user_data.Rdata"))
  
relevant_user <- user_data %>%
  filter(datatype == "user_profile") %>%
  inner_join(unique_user_content, by = c("id" = "creator"), keep = TRUE) %>%
  select(-c("id", "key"))

save(relevant_user, file = str_c(path_output, "relevant_user.Rdata"))

```

# Preprocess user bios

```{r preprocess user bios, include = FALSE}

## Filter English speaking users (bio in English => user English-speaking)
user_bio <- relevant_user %>%
  select(creator, bio) %>%
  filter(bio != "") %>%
  mutate(bio = replace_contraction(bio, contraction.key = lexicon::key_contractions),
         bio = str_remove_all(bio, pattern = "#"),
         bio = str_to_lower(bio),
         language_2 = cld2::detect_language(bio),
         language_3 = cld3::detect_language(bio)) %>%
  filter(language_2 == "en" | language_3 == "en") %>%
  mutate(user_id = row_number())

save(user_bio, file = str_c(path_output, "user_bio.Rdata"))

# Annotate bios with udpipe model
splits <- 1000
# Split dataset for parallelization
bios_split <- split(user_bio, (seq(nrow(user_bio))-1) %/% splits)
annotation <- bios_split %>%
  future_map(annotate_splits, var = "bio", .progress = TRUE, .options = furrr_options(seed = TRUE)) %>%
  future_map(~ mutate(.x, doc_id = as.numeric(str_remove(doc_id, pattern = "doc"))))

# Fix document numbering
for (i in 2:length(annotation)) {
  annotation[[i]] <- annotation[[i]] %>%
    mutate(doc_id = doc_id+(i-1)*splits)
}

bios_annotated <- bind_rows(annotation)

save(bios_annotated, file = str_c(path_output, "bios_annotated.Rdata"))

# Clean annotated bios
tidy_bios <- bios_annotated %>%
  select(doc_id, token, upos) %>%
  mutate(token = str_to_lower(token, locale = "en"),
         token_lag = lag(token),
         # Handle split of "wwg1wga"
         token = if_else(str_detect(token, pattern = "wwg") & str_detect(lead(token), pattern = "1") & str_detect(lead(token, n = 2), pattern = "wga"), "wwg1wga", token, missing = token),
         upos = if_else(token == "1" & lag(token) == "wwg1wga" & lead(token) == "wga", "DROP", upos, missing = token),
         upos = if_else(token == "wga" & lag(token, n = 2) == "wwg1wga" & lag(token) == "1", "DROP", upos, missing = token),
         token = if_else(token == "wwg1" & lead(token) == "wga", "wwg1wga", token, missing = token),
         upos = if_else(token == "wga" & lag(token) == "wwg1wga", "DROP", upos, missing = token),
         token = if_else(str_detect(token_lag, pattern = "^@$|^#$"), str_c(token_lag, token, sep = ""), token, missing = token),  
         upos = if_else(str_detect(token, pattern = "@|#"), "X", upos), # label # -> X, @ -> X
         upos = if_else(str_detect(token, pattern = "^@$|^@@$|^#$|^##$"), "DROP", upos),
         upos = if_else(str_detect(token, pattern = "^\\d$"), "NUM", upos),
         token = if_else(str_detect(token, pattern = "&") & upos == "CCONJ", "and", token), # "&" to "and"
         token = str_replace_all(token, pattern = "[^\x01-\x7F]", "")) %>% # Remove Emojis
  select(-c(token_lag)) %>%
  left_join(user_bio, by = c("doc_id" = "user_id")) %>% # merge creator
  rename(user_id = doc_id) %>%
  select(-c(bio)) %>%
  filter(!str_detect(token, pattern = "^@$|^#$") 
         & !str_detect(token, pattern = "^'s$")
         & upos != "PUNCT" 
         & upos != "DROP" 
         & upos != "SYM"
         & upos != "NUM") %>% # Filter punctuation, single @/#, Symbols/Emojis, Numbers
  mutate(token = str_replace_all(token, c("^n't$|^n't$|^nt$" = "not", 
                                          "^'m$" = "am",
                                          "^'re$" = "are",
                                          "^'ll$" = "will",
                                          "^'ve$" = "have",
                                          "#|@" = "")),
         token = str_remove_all(token, pattern = "\\.|\\?|\\!|\\:|[:blank:]")) %>%
  filter(token != "") %>%
  anti_join(stop, by = c("token" = "word"))

save(tidy_bios, file = str_c(path_output, "tidy_bios.Rdata"))

```

# QAnon Identification

```{r}

# Classify QAnon vs. non-QAnon
user_qanon <- user_bio %>%
  mutate(bio = str_to_lower(bio),
         bio = str_remove_all(bio, "@[a-z,A-Z,0-9]*"), # Remove handles
         bio = str_remove_all(bio, "[^\x01-\x7F]"), # Remove emojis
         bio = str_remove_all(bio, "#"), # Remove "#"
         qIndicator = if_else(str_detect(bio, pattern = str_c(qanon_indicator, collapse = "|")), 1, 0)) %>%
  select(creator, qIndicator)

save(user_qanon, file = str_c(path_output, "user_qanon.Rdata"))

user_bio_qanon <- user_qanon %>%
  select(creator, qIndicator) %>%
  right_join(tidy_bios, by = "creator")
  
save(user_bio_qanon, file =  str_c(path_output, "user_bio_qanon.Rdata"))


```

# Create user data

```{r}

# Match relevant user profiles with user data
data_qanon_user <- user_data %>%
  inner_join(user_qanon, by = c("id" = "creator")) %>%
  select(-key) %>%
  rename(creator = id)

save(data_qanon_user, file = str_c(path_output, "data_qanon_user.Rdata"))

```

# Preprocess parleys

```{r preprocess parleys, include = FALSE}

# Tidy parleys text only no stopwords
tidy_parleys_text <- tidy_parleys_annotated %>%
  ungroup(comment_id, creator) %>%
  select(comment_id, token, qIndicator) %>%
  anti_join(stop, by = c("token" = "word"))

save(tidy_parleys_text, file = str_c(path_output, "tidy_parleys_text.Rdata"))

```

# Feature creation

```{r}

# Load helper functions for text embeddings
source("Helpers_feature_creation.R")

# Set up parallel processing
plan(multisession, workers = 13)

```


```{r embeddings, include=false}

# Clean text for calculation of embeddings
file_list_content_by_user %>%
  future_map(~ clean_text_embedding(.x, path_input = str_c(path_input, "parleys_user/"), path_output = str_c(path_input, "parleys_user/clean_text/")))

# Compute embeddings -> shifted to Python (see file Parler_text_embeddings.py)
# list.files(path = str_c(path_input, "parleys_user/clean_text/"), pattern = "*.RDS") %>%
#   future_map(~ compute_embeddings(.x, path_input = str_c(path_input, "parleys_user/clean_text/"), path_output = str_c(path_output, "embeddings_raw/")),
#              furrr_options(seed = TRUE))
  
# Aggregate embeddings
list.files(path = str_c(path_output, "embeddings_raw/"), pattern = "*.csv") %>%
  future_map(~ aggregate_embeddings(.x, path_input = str_c(path_output, "embeddings_raw/"), path_output = str_c(path_output, "embeddings_aggregated/")))
  
# Concatenate files
features_bert <- list.files(path = str_c(path_output, "embeddings_aggregated/"), pattern = "*.RDS") %>%
  future_map_dfr(~ read_rds(str_c(path_output, "embeddings_aggregated/", .x)))

# Save features Bert
saveRDS(features_bert, file = str_c(path_output, "features_bert.RDS"))

```

# Annotation of text data

```{r annotation, include=false}

list.files(path = str_c(path_input, "parleys_user/"), pattern = "*.RDS") %>%
  future_map(~ annotate_text(.x, path_input = str_c(path_input, "parleys_user/"), path_output = str_c(path_output, "annotation/")),
             furrr_options(seed = TRUE))

## For large files (3/639) 
# Memory not sufficient => split files and annotate sequentially
# Load files
total <- seq(1:length(list.files(path = str_c(path_output, "annotation/"), pattern = "*RDS")))
files <- parse_number(list.files(path = str_c(path_output, "words/"), pattern = "*.RDS"))
missing <- total[-files]
files_missing <- str_c("user_content_", missing, ".RDS")

for (i in 1:length(files_missing)){
  dta <- read_rds(str_c(path_input, "parleys_user/", files_missing[i])) %>%
    select(creator, body, id) %>%
    mutate(comment_id = row_number())
  
  # Annotate bios with udpipe model
  splits <- 200000
  # Split dataset for parallelization
  content_split <- split(dta, (seq(nrow(dta))-1) %/% splits)
  annotation <- content_split %>%
    future_map(annotate_splits, var = "body", .progress = TRUE, .options = furrr_options(seed = TRUE)) %>%
    future_map(~ mutate(.x, doc_id = as.numeric(str_remove(doc_id, pattern = "doc"))))
  
  # Fix document numbering
  for (j in 1:length(annotation)) {
    annotation[[j]] <- annotation[[j]] %>%
      mutate(doc_id = doc_id+(j-1)*splits)
  }
  
  content_annotated <- bind_rows(annotation)
  
  tidy_parleys_annotated <- content_annotated %>%
    mutate(token = str_to_lower(token, locale = "en"),
           token_lag = lag(token),
           # Handle split of "wwg1wga"
           token = if_else(str_detect(token, pattern = "wwg") & str_detect(lead(token), pattern = "1") & str_detect(lead(token, n = 2), pattern = "wga"), "wwg1wga", token, missing = token),
           upos = if_else(token == "1" & lag(token) == "wwg1wga" & lead(token) == "wga", "DROP", upos, missing = token),
           upos = if_else(token == "wga" & lag(token, n = 2) == "wwg1wga" & lag(token) == "1", "DROP", upos, missing = token),
           token = if_else(token == "wwg1" & lead(token) == "wga", "wwg1wga", token, missing = token),
           upos = if_else(token == "wga" & lag(token) == "wwg1wga", "DROP", upos, missing = token),
           token = if_else(str_detect(token_lag, pattern = "^@$|^#$"), str_c(token_lag, token, sep = ""), token, missing = token), # merge single @/# with next line 
           upos = if_else(str_detect(token, pattern = "@|#"), "X", upos), # label # -> X, @ -> X
           upos = if_else(str_detect(token, pattern = "^@$|^@@$|^#$|^##$"), "DROP", upos),
           token = if_else(str_detect(token, pattern = "&") & upos == "CCONJ", "and", token), # "&" to "and"
           token = str_replace_all(token, pattern = "[^\x01-\x7F]", "")) %>% # Remove Emojis
    select(-token_lag) %>%
    left_join(dta, by = c("doc_id" = "comment_id")) %>% # merge creator
    rename(comment_id = doc_id) %>%
    select(-c(body, id)) %>%
    filter(!str_detect(token, pattern = "^@$|^#$") 
           & !str_detect(token, pattern = "^'s$")
           & upos != "PUNCT" 
           & upos != "DROP" 
           & upos != "SYM"
           & upos != "NUM") %>% # Filter punctuation, single @/#, Symbols/Emojis, Numbers
    group_by(comment_id, creator) %>%
    mutate(token = str_replace_all(token, c("^n't$|^n't$|^nt$" = "not", 
                                            "^'m$" = "am",
                                            "^'re$" = "are",
                                            "^'ll$" = "will",
                                            "^'ve$" = "have")),
           token = str_remove_all(token, pattern = "\\.|\\!|\\?")) %>%
    filter(token != "")
  
  saveRDS(tidy_parleys_annotated, file = str_c(path_output, "annotation/", "annotated_content_", parse_number(files_missing[i]), ".RDS"))
}


```

# Linguistic features

```{r, linguistic, include=false}

# Features from parleys (i.e. freq of handles, hashtags, pos-tags, long words)
list.files(path = str_c(path_input, "parleys_user/"), pattern = "*.RDS") %>%
  future_map2(.y = list.files(path = str_c(path_output, "annotation/"), pattern = "*.RDS"),
                  ~ create_linguistic_meta_content(.y, .x, path_input = path_input, path_output = str_c(path_output, "linguistic/")))

features_linguistic <- list.files(path = str_c(path_output, "linguistic"), pattern = "*.RDS") %>%
  future_map_dfr(~ read_rds(str_c(path_output, "linguistic/", .x)))

features_linguistic <- features_linguistic %>%
  mutate(across(.cols = c(-creator), as.numeric))#,
         #across(.cols = c(-creator), scale),
         #across(.cols = c(-creator, -set), ~ if_else(is.na(.x), 0, .x)))

features_linguistic <- features_linguistic %>%
  left_join(user_qanon, by = "creator")

save(features_linguistic, file = str_c(path_output, "features_linguistic.Rdata"))

```

# User features

```{r user features, include=false}

# Create features from user metadata
## Features include: # followers, # following, # comments, # posts, account age
features_user <- data_qanon_user %>%
  rename(user_comments = comments, user_posts = posts) %>%
  mutate(joined = ymd_hms(joined),
         account_age = ymd_hms("20210201000000") - joined) %>% # Compute account as of 1st February 2021
  mutate(across(.cols = c(-creator, -qIndicator, -bio, -datatype), .fns = as.numeric))#,
         #across(.cols = c(-creator, -qIndicator), .fns = scale),
         #across(.cols = c(-creator, -qIndicator, -bio, -datatype), ~ if_else(is.na(.x), 0, .x)))

save(features_user, file = str_c(path_output, "features_user.Rdata"))
  
```

# Feature sets

```{r features sets, include=FALSE}

# Combine all features
features_all_unalterd <- features_bert %>%
  left_join(features_user, by = "creator") %>%
  select(-qIndicator) %>%
  inner_join(features_linguistic, by = "creator")

save(features_all_unalterd, file = str_c(path_output, "features_all_unscaled.Rdata"))
  
# Scale features
features_all <- features_all_unalterd %>%
  mutate(across(.cols = c(-creator, -qIndicator, -names_features_text, -bio, -datatype, -set), ~ if_else(is.na(.x), 0, .x)),
         across(.cols = c(-creator, -qIndicator, -names_features_text, -bio, -datatype, -set), ~ scale(.x)),
         across(.cols = c(-creator, -qIndicator, -names_features_text, -bio, -datatype, -set), ~ as.vector(.x))) %>%
  select(creator, qIndicator, all_of(names_features_all))

save(features_all, file = str_c(path_output, "features_all.Rdata"))

```
